---
title: "Introduction to EMMultiOmics Package"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{gene_grouping}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup, echo=FALSE, results=FALSE, message=FALSE}
library(EMMultiOmics)
```

## Outline

- Purpose of the package
- Brief explanation of the algorithms and workflow
- description of example data used
- DAVID functional classification tool
- 1st stage modeling with `EMVS()`
- 2nd stage modeling with `NEG_em()`
- summary of the model results and plots

## 1. Purpose

...

## 2. Algorithms

...

## 3. example data

We will be working with GBM data from ... Example gene symbols are stored in `eg_gene_symbols.` To obtain gene grouping, we need to get functional classification of these from DAVID.


## 4. David functional classifcation tool

`vignette("gene_grouping")`

Once the classification file is downloaded as txt, use `get_grouping()` function to obtain the gene grouping.

```{r, eval=FALSE}
fp <- system.file("eg_fx_classification.txt", package="EMMultiOmics")
gene_grouping <- get_grouping(eg_gene_symbols, fp)
gene_grouping
```

## 5. 1st stage modeling

Example on how to use `EMVS()`


## 6. 2nd stage modeling

Example on how to use `NEG_em()`.
How to get 



## 7. summary



